% vim:tw=76
\documentclass[a4paper,12pt]{report}
\usepackage{a4wide,pslatex,url}
\usepackage[compact]{titlesec}
\setlength{\parindent}{0em}
\setlength{\parskip}{0.5em}

\begin{document}

    \section*{\centering Colin Watson}

    \begin{tabular}{l l}
        Address & 15 High Street, Wilburton, Ely, CB6 3RB, United Kingdom \\
        E-mail & cjwatson@chiark.greenend.org.uk \\
        Telephone & On request \\
        Nationality & British, Irish \\
    \end{tabular}

    \addvspace{1em}

    I am a self-starting free software developer who has been a core member of
    the Debian and Ubuntu development teams for many years. I like delivering
    software to end users and actually maintaining it afterwards. Experience
    working at the scale of large software distributions has taught me how to
    navigate and absorb unfamiliar codebases very quickly, particularly build
    systems. I have worked remotely for the majority of my professional life,
    have a strong sense of personal responsibility, and do not require close
    supervision to remain productive.

    \subsection*{Employment}

    Jan 2015 -- present day: \nopagebreak\\
    Software Engineer on Canonical's Launchpad team. Projects included: adding
    Git hosting support; rewrote much of launchpad-buildd for improved
    testability; building snap and charm recipes; adding GitHub bug linking;
    several Twisted improvements to support newer SSH protocol features;
    revamping build system; implementing a code-signing service; mentoring
    several new engineers; and porting the main \textgreater{}700KLoC codebase
    to Python 3.

    Oct 2008 -- Dec 2014: \nopagebreak\\
    Technical Lead for the Ubuntu Foundations team. Projects included:
    significant contributions to GRUB 2; flicker-free boot; a large part of
    Ubuntu's implementation of UEFI Secure Boot; cross-building packages at
    scale; improved the quality of daily builds, including starting a rotating
    maintenance squad and shifting uploads to a staged model; service on the
    Technical Board; porting various packages to Python 3; and a great deal of
    maintenance work.

    Dec 2006 -- Oct 2008: \nopagebreak\\
    Ubuntu Development Manager for Canonical, responsible for the Ubuntu
    Foundations team.

    May 2004 -- Dec 2006: \nopagebreak\\
    Joined Canonical Ltd. as one of its initial group of developers of the
    Ubuntu distribution of GNU/Linux. Projects included: initiating and leading
    the installer team; building CD images; a stint as release manager;
    development and maintenance of various archive-related software; and the
    creation of a new graphical installer.

    May 2003 -- May 2004: \nopagebreak\\
    Software Engineer for nCipher Corporation, Cambridge. Worked on improving
    ASN.1 support, bug tracking system infrastructure, and the beginnings of a
    TPM-related project.

    August 2000 -- April 2003: \nopagebreak\\
    Software Engineer for Zeus Technology, Cambridge, specialising initially in
    performance and later in web server development. Experience in Unix
    performance tuning, C++, and Perl (both scripting and XS). Primary author of
    the Perl extensions to the Zeus Web Server.

    June--September 1999: \nopagebreak\\
    Summer job in C development (configuration management for embedded
    communications software) at Data Connection, London.

    \subsection*{Other Experience}

    Self-taught C, Perl, Python, and various other less useful languages, as
    well as some university-taught programming. I took part in several
    maths/programming competitions as a student, and was twice a member of
    Ireland's International Olympiad in Informatics team.

    Unix development (both out of personal interest and professionally), and
    competency in Linux administration (Debian, Ubuntu).

    In February 2001 I became a developer for the Debian Project
    (\url{https://www.debian.org/}). I currently maintain, among others, the
    man-db, groff, and ctags packages; I wrote various packages such as
    binfmt-support and libpipeline from scratch; I co-maintain openssh and
    grub2; and I am a (now largely inactive) member of the team which
    administers the bug tracking system. I served on the Debian Technical
    Committee from August 2011 to March 2015.

    I am married with four children.

    I have held a full UK driving licence since 1996, free from endorsements.

    I have a classical music background, with training in piano and cello,
    although these days most of my musical activity is singing; I am an
    occasional cantor at our local church.

    \subsection*{Education}

    1997-2000: Trinity College, Cambridge \\
    1990-1997: Our Lady and St.\ Patrick's College, Knock

    \subsection*{Academic Qualifications}

    12 GCSEs (9 A*s, 3 As); 4 A-levels (4 As); 1 AS (A); 2 STEPs (S in
    Mathematics II, 1 in Mathematics III).

    BA (Hons) reading Computer Science at Trinity College, Cambridge; classed as
    I/I/II.2.

    \addvspace{1em}

    Copies of this CV in other formats are available at
    \url{https://www.chiark.greenend.org.uk/~cjwatson/cv/}.

    Last modified: \verb'$Date: 2021-11-06 02:24:17 +0000 $'

\end{document}