\documentclass{resume}
\DeclareSymbolFont{extraup}{U}{zavm}{m}{n}
\DeclareMathSymbol{\varheart}{\mathalpha}{extraup}{86}
\DeclareMathSymbol{\vardiamond}{\mathalpha}{extraup}{87}
\usepackage{url}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\pagestyle{plain}
\pagenumbering{gobble}
\begin{document}
	\begin{rSection}{Federico Viscomi's CV}
		I'm a mindful software engineer and I care about coding.
		%have an MSc computer science degree with full marks and honours, 
		%a fair amount of experience with software development working at the core business of world class employers 
		%and I am passionate about experimenting with new technologies.
	\end{rSection}
	\begin{rSection}{Career history and qualifications}
		{\bf Cisco International Ltd, Staines UK} \hfill {\em 04/2016 $\rightarrow$  present}\\
			System integration and embedded C and Java engineer. 
			My main task is investigating issues on Sky set-top boxes and propose bug fixes. 
			We make extensive use of Python and Splunk for analysis of machine data to aid issue investigation.
			TODO add number of customer that the project Darwin I'm owrking on has! to show the impact!!!

		{\bf Qualcomm UK Ltd, Farnborough UK} \hfill {\em 05/2014 $\rightarrow$ 04/2016}\\
			I was a member of the cryptography and security team and I have contributed to designing writing testing and reviewing the following kinds of software:
			Android applications for showcasing services and libraries to our b2b customers,
			Android services, 
			Java and JNI libraries, 
			C/C++ libraries such as PKCS11 compliant cryptographic libraries,
			C/C++ system daemons,
			trusted applications for Qualcomm's TrustZone based real time operating system,
			C libraries at the kernel level,
			Python programs for manipulation of binary files and for collecting analysing and visualising data.	
			%Not only have I taken part in the realization of new projects but I have contributed to exiting projects with a large code base as well.
			%On the people management side I was responsible for getting up to speed a new hire.

		{\bf eBay International Marketing GmbH, Z\"urich, CHE} \hfill {\em 09/2013 $\rightarrow$ 03/2014}\\
			Web developer in agile teams. 
			We followed losely a TDD process. 
			We used HTML5, JavaScript and AngularJS for the front-end. 
			The back-end used Java or Scala with the Play framework and was backed by a MySQL database or a MongoDB. 
			Other technologies we used are: 
			REST; TestNG for testing the back-end; 
			Jenkins for continuous integration; 
			Gerrit for code review; 
			GIT as version control system; 
			maven and sbt for build automation;
			websocket for communication among front-end and back-end.	  
	    
			%I am particularly proud of a project called TweetMiner, 
			%I and two other interns started this project from scratch,
			%it is a web application that uses data mining, pattern recognition and sentiment analysis 
			%techniques on tweets to find out how people feel about eBay and the products they bought. 

		{\bf MSc in Computer Science full marks with honours} \hfill {\em 09/2010 $\rightarrow$ 03/2013} \\
		Universit\`a di Bologna and Freie Universit\"at Berlin 
		%Subjects:
		%Program analysis, Concurrent models and systems, Lambda calculus,
		%Type theory, Cryptography, Artificial intelligence, Digital signal processing,
		%Advanced algorithms, Functional programming in OCaml, Computational mathematics with Wolfram Mathematica\\

		{\bf National Research Council of Italy, Pisa Italy} \hfill {\em 02/2009 $\rightarrow$ 10/2009}\\
			Research intern on big data and semantic web.
			%I built a deductive system for an extension of RDF with fuzzy logic under the supervision of a senior researcher Umberto Straccia.
			%The work I have done include:
			%an implementation of a new language fuzzyRDF as a particular subset of RDF,
			%a mechanisms of storage of RDF knowledge bases as XML files,
			%a graphical and textual interface to the system,
			%a proper configuration of the deductive rules of the Apache Jena reasoner,
			%definition of the syntax of an apposite new query language: Fuzzy RDF Query language (FuRQL)
			%and implementation in Java of a parser and a compiler from FuRQL to the SPARQL language 

		{\bf BSc in Computer Science full marks} Universit\`a di Pisa \hfill {\em 09/2006 $\rightarrow$ 10/2009} \\
		%Subjects: 
		%Algebra, Mathematical analysis, Numerical calculus, Operational research,
		%Probability and statistics, Classical mechanics, Computational physics,
		%Java memory model and semantic, Algorithms and data structures, Relational databases,
		%Operating systems, Computer architectures, Artificial intelligence, Principle of compilers and interpreter design,
		%Automaton and grammars theory, UML and software development processes, Computer networks,
		%Data structure programming laboratory in Java, Network and multithreaded programming laboratory in Java,
		%C programming laboratory, Concurrent and operating systems programming laboratory in C,
		%PROLOG programming, SQL programming
	\end{rSection}
	\footnote{Updated \today}
\end{document}
