\documentclass{resume}
\DeclareSymbolFont{extraup}{U}{zavm}{m}{n}
\DeclareMathSymbol{\varheart}{\mathalpha}{extraup}{86}
\DeclareMathSymbol{\vardiamond}{\mathalpha}{extraup}{87}
\usepackage{url}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\pagestyle{plain}
\pagenumbering{gobble}
\begin{document}
	\begin{rSection}{Federico Viscomi - Mindful software engineer}
		I have an MSc computer science degree with full marks and honours, 
		a fair amount of experience with software development working at the core business of world class employers 
		and I am passionate about experimenting with new technologies.

	\end{rSection}
	\begin{rSection} {Contact details}
                email: federicoviscomi@gmail.com,
		phone number: +447801273266,
                address: Staines, Surrey, UK
	\end{rSection}
	\begin{rSection}{Career history and qualifications}
		{\bf Cisco International Ltd, Staines UK} \hfill {\em 04/2016 $\rightarrow$ present}\\
			System integration and embedded C and Java engineer. 
			My main task is investigating issues on Sky set-top boxes and propose bug fixes.
			%I contribute to development and maintenance of our internal tools and websites some of which are written in Python on the flask framework.
			I make use of Python and Splunk for analysis of machine data to aid issue investigation.

		{\bf Qualcomm UK Ltd, Farnborough UK} \hfill {from \em 05/2014, 2 years contract}\\
			I was a member of the cryptography and security team and I have contributed to designing writing testing and reviewing the following kinds of software:
			Android applications for showcasing services and libraries to our b2b customers,
			Android services, 
			Java and JNI libraries, 
			C/C++ libraries such as PKCS11 compliant cryptographic libraries,
			C/C++ system daemons,
			trusted applications for Qualcomm's TrustZone based real time operating system,
			C libraries at the kernel level,
			Python programs for manipulation of binary files and for collecting analysing and visualising data.	
			Not only have I taken part in the realization of new projects but I have contributed to exiting projects with a large code base as well.
			On the people management side I was responsible for getting up to speed a new hire.

		{\bf eBay International Marketing GmbH, Z\"urich, CHE} \hfill {from \em 09/2013, 6 months internship}\\
			Web developer intern in agile teams.
			We followed loosely a TDD process.
			We used HTML5, JavaScript and AngularJS for the front-end. 
			The back-end used Java or Scala with the Play framework and was backed by a MySQL database or a MongoDB. 
			Other technologies we used are: 
			REST; TestNG for testing the back-end; 
			Jenkins for continuous integration; 
			Gerrit for code review; 
			GIT as version control system; 
			maven and sbt for build automation;
			websocket for communication among front-end and back-end.	  
	    
			%I am particularly proud of a project called TweetMiner, 
			%I and two other interns started this project from scratch,
			%it is a web application that uses data mining, pattern recognition and sentiment analysis 
			%techniques on tweets to find out how people feel about eBay and the products they bought. 

		{\bf MSc in Computer Science full marks with honours} \hfill {\em from 09/2010, 2 years plus one semester delay} \\
		Universit\`a di Bologna and Freie Universit\"at Berlin 
		%Subjects:
		%Program analysis, Concurrent models and systems, Lambda calculus,
		%Type theory, Cryptography, Artificial intelligence, Digital signal processing,
		%Advanced algorithms, Functional programming in OCaml, Computational mathematics with Wolfram Mathematica\\

		{\bf National Research Council of Italy, Pisa Italy} \hfill {from \em 02/2009, 6 months internship}\\
			Researcher intern on semantic web and big data.
			%I built a deductive system for an extension of RDF with fuzzy logic under the supervision of a senior researcher Umberto Straccia.
			%The work I have done include:
			%an implementation of a new language fuzzyRDF as a particular subset of RDF,
			%a mechanisms of storage of RDF knowledge bases as XML files,
			%a graphical and textual interface to the system,
			%a proper configuration of the deductive rules of the Apache Jena reasoner,
			%definition of the syntax of an apposite new query language: Fuzzy RDF Query language (FuRQL)
			%and implementation in Java of a parser and a compiler from FuRQL to the SPARQL language 

		{\bf BSc in Computer Science full marks} Universit\`a di Pisa \hfill {\em from 09/2006, 3 years right on time} \\
		%Subjects: 
		%Algebra, Mathematical analysis, Numerical calculus, Operational research,
		%Probability and statistics, Classical mechanics, Computational physics,
		%Java memory model and semantic, Algorithms and data structures, Relational databases,
		%Operating systems, Computer architectures, Artificial intelligence, Principle of compilers and interpreter design,
		%Automaton and grammars theory, UML and software development processes, Computer networks,
		%Data structure programming laboratory in Java, Network and multithreaded programming laboratory in Java,
		%C programming laboratory, Concurrent and operating systems programming laboratory in C,
		%PROLOG programming, SQL programming
	\end{rSection}
	\begin{rSection}{}
		Updated \today.
	\end{rSection}
\end{document}
